\pdfbookmark[0]{English title page}{label:titlepage_en}
\aautitlepage{%
  \englishprojectinfo{
    Path Finding%title
  }{%
    Microprocessor based Systems%theme
  }{%
    Fall Semester 2017 %project period
  }{%
    ED3-1-E17 % project group
  }{%
    %list of group members
    Daniel Frederik Busemann\\ 
    Razvan-Vlad Bucur\\
    Troels Ulstrup Klein
  }{%
    %list of supervisors
    Akbar Hussain\\
  }{%
    1 % number of printed copies
  }{%
    \today % date of completion
  }%
}{%department and address
  \textbf{Electronics and Computer Engineering}\\
  Aalborg University\\
  \href{http://www.aau.dk}{http://www.aau.dk}
}{% the abstract
	This report describes robotic path-finding in a fictional rescuing scenario.
	
	The theory got tested on a microcontroller-based robot.
	A system design for a robot was made,
	based on a set of requirements.
	The functionality of the subsystems gets explained more thoroughly in their own chapters,
	going into all relevant details.
	
	Movement includes a brief overview over stepper motor technologies
	and our specific circuits to handle them.
	
	Map Handling explains the internal handling of a dynamically changing map,
	going into detail about the necessary programming.
	
	Scan evaluates different options to monitor the environment,
	explaining the chosen solution in detail.
	
	Pathfinding discusses different algorithms,
	explaining how they relate to each other,
	what functionality to consider for grid-based maps,
	and goes into detail about how the final choice was made.
}

\cleardoublepage